---
title:  "Learning StandaRtox - A basic introduction for beginners"
author: "Hannes Reinwald, Andreas Scharmüller, Heike Fremdt"
date:   "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    toc: true
    toc_float: true
runtime: shiny
---

----

# Setting up your R environment

### Installing packages
First we need to install the *standartox* package for R. This can be easily done by running the following code in your R console:
```{r, eval=FALSE}
if (!requireNamespace("standartox", quietly = TRUE)) { # <- this checks if the package is already installed
  install.packages("standartox")
}
```

The *standartox* package depends on the data.table package, which is a powerful R-package for efficient data manipulation. Hence, it is also required for the *standartox* package to work properly. If you don't have it installed, you can do so with the following command:
```{r, eval=FALSE}
if (!requireNamespace("data.table", quietly = TRUE)) { # <- this checks if the package is already installed
  install.packages("data.table")
}
```

### Loading packages
If we have the required R-packages installed we must load them into our current R session. It is good practice to load all required packages at the beginning of your R script. This way you can easily see which packages are needed for your analysis. The following code loads the *standartox* and *data.table* packages:
```{r}
library(standartox)
library(data.table)
```

----

# The StandaRtox Architecture
Show the basic functionalists of the following standartox functions:

  - `stx_download()`
  - `stx_catalog()`
  - `stx_chem()`
  - `stx_taxa()`
  - `stx_data()`
  - `stx_query()`

### stx_download()
The backbone of any database call or query is the database itself. The *standartox* package itself does not come with a built-in database.
Instead, it provides a function to download the StandaRtox relational database files from [Zenodo.org](https://doi.org/10.5281/zenodo.3785030) 

This database is stored in a specific directory on your computer, which is defined by the `stx_dir` parameter. The default directory is set to a temporary directory (`file.path(tempdir(),"standartox")`), which is automatically deleted when you closing your R-Session. 
```{r, eval=FALSE}
# By default standartox will download the StandaRtox database into stx_dir = file.path(tempdir(),"standartox") 
stxDb = standartox:::stx_download(silent = FALSE) # <- this will store your Db files in a tmp directory 
list.files(file.path(tempdir(),"standartox"))
```

If you wish to keep the standartox data base files permanently on your device you can specify any directory on your system. 
```{r, eval=FALSE}
# If you wish to keep the downloaded data base permanently, you can specify your storage directory.
local_stx_dir = "~/standartox"
stxDb = standartox:::stx_download(silent = FALSE, stx_dir = local_stx_dir)
list.files(local_stx_dir) 
```

Before running any query, standartox will first check if it can find the required data base files on your local system (specified in `stx_dir`). If it finds the files it will not launch the download from Zenodo. Hence, the download (which might take a while) is only needed once. After that it will run the querries on your local files system which is much faster. 

**The good news is that we don't have to use `stx_download()` itself if we wish to query standartox data base!** This function is embedded in in the subsequent functions. Hence, to keep your life simple you can directly go to a query via `stx_query()` or inspect the data catalog via `stx_catalog`.

### stx_catalog()
```{r, eval=FALSE}
catalog = stx_catalog()
```

### stx_chem()
```{r, eval=FALSE}
chem.dt = stx_chem()
```

### stx_taxa()
```{r, eval=FALSE}
taxa.dt = stx_taxa()
```

### stx_data()
```{r, eval=FALSE}
tox.dt = stx_data()
```

### stx_query()
```{r, eval=FALSE}
qres = stx_query()
```

----
  
# Running **stx_query()**





