---
title: "Research qustions - Hacking StandaRtox"
output: github_document
---

## Setup

```{r setup}
# remotes::install_github('andschar/standartox')
require(standartox)
require(dplyr)
require(ggplot2)
require(udunits2)
```

## Data

```{r pressure, echo=FALSE}
# Load data
stx = standartox::stx_data()
che = standartox::stx_chem()
tax = standartox::stx_taxa()
# Merge data
dat = merge(stx, tax, by = 'tl_id')
dat = merge(dat, che, by = 'casnr')
```

## Research qustions

### Most common taxa (genus level) & chemical combination

What are the most common taxa in the dataset?

```{r}

```

### Most tested pesticide class

What is the most tested pesticide class in the dataset?

Hint: Extract the pesticide class from the chem_class column via regex.

### Daphnia life stage vulnerability

Which Daphnia life stage is the most vulnerable against insecticides?

- More filters
    - Endpoints: EC50, LC50
    - Effect: mortality, intoxication
    - Life stages: Neonates, Larava, Juvenile and Adult.

Mind the units!

```{r}

```

### What are the chemicals with the most tested taxa?